### 2019-08-26 boek.tex
refactorise

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{ch4_dyno}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{ch5_scorpius}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH6: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{ch6_brood}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH8: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\include{ch8_discussion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH4: DYNO         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{dyno: A toolkit for inferring and interpreting trajectories} 
\chaptermark{dyno: A toolkit for inferring and interpreting trajectories.} % short title
\label{chap:dyno}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. dyno: A toolkit for inferring and interpreting trajectories. \textit{Journal} vol, issue (2019), page--page. doi.
\include{ch4_dyno/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%       CH5: SCORPIUS       %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{SCORPIUS: Fast, accurate, and robust single-cell pseudotime} 
\chaptermark{SCORPIUS: Fast, accurate, and robust single-cell pseudotime.} % short title
\label{chap:scorpius}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, \ldots, De Preter, K., and Saeys, Y. SCORPIUS improves trajectory inference and identifies novel modules in dendritic cell development. \textit{Journal} vol, issue (2019), page--page. \doi{10.1101/079509v2}.
\newpage
\include{ch5_scorpius/content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%         CH6: BRED         %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{bred: Inferring single cell regulatory networks} 
\chaptermark{bred: Inferring single cell regulatory networks.} % short title
\label{chap:bred}
\begin{quote}
	\textbf{Abstract:} \blindtext
\end{quote}
\vfill
Adapted from:\\
\textbf{Cannoodt, R.}, Saelens, W., and Saeys, Y. Inferring Single Cell Regulatory Networks. \textit{Journal} vol, issue (2019), page--page. doi.
\newpage
\include{ch6_bred/content}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%      CH8: DISCUSSION      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{\thispagestyle{empty}\cleardoublepage}
\chapter{General discussion} 
\chaptermark{General discussion.} % short title
\label{chap:discussion}
\include{ch8_discussion/content}
